Community comparison

### 2019-11-29 code/community.Rmd
dark theme for omics presentation

```{r globals, include=F}
# define theme for all heatmaps
my_heat_theme <- theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x=element_blank())
```

@@

ggsave(here("manuscript/figs/main/community/community_ggplot.pdf"), plot=community_heatmap, width=7, height=4)
```

>>>>

```{r globals, include=F}
# define theme for all heatmaps
my_heat_theme <- theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x=element_blank())
theme_set(dark_theme_light())
```

@@

# presentation output
ggsave(here("presentation/omics/community_ggplot.pdf"), plot=community_heatmap, width=7, height=4)
```
